Introduction

### 2012-10-25 dissertation/tmpsolutions.tex
minor
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@414 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{verbatim}
_:foo void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects lang:nb .
].
\end{verbatim}
This would declare \rdfterm{lang:nb} as the most frequent object for
\rdfterm{dct:language}, and this simple example would solve the
\langcase.

@@

Another option would be to do something like:
\begin{verbatim}
_:foo void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects 
    [
      void:object lang:nb ;
      void:frequency "0.012" .
    ]
].
\end{verbatim}
but this solution would be less general but of similar complexity than
the nested solution above.

@@

Some time ago, I wrote a partial paper about how fully indexed stores
like Hexastore \cite{hexastore} could easily find the cardinality of
any given triple pattern. It would be interesting to publish that soon
in some form.

@@

Amongst the below references, the most important are
\cite{selectivityPRM}, \cite{Lin:2011:LRB:2063016.2063042} and
\cite{splendid}.

>>>>

\begin{verbatim}
</foo> void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects lang:nb .
].
\end{verbatim}
This would declare \rdfterm{lang:nb} as the most frequent object for
\rdfterm{dct:language}, and this simple example would solve the
\langcase.

@@

Another option would be to do something like:
\begin{verbatim}
</foo> void:propertyPartition 
  [
    void:property dct:language ;
    void:mostFrequentObjects 
    [
      void:object lang:nb ;
      void:frequency "0.012" .
    ]
].
\end{verbatim}
but this solution would be less general but of similar complexity than
the nested solution above.

@@

Some time ago, I wrote a partial paper about how fully indexed stores
like Hexastore \cite{Weiss:2008:HSI:1453856.1453965} could easily find the cardinality of
any given triple pattern. It would be interesting to publish that soon
in some form.

@@

Amongst the below references, the most important are
\cite{selectivityPRM}, \cite{splendid} and \cite{Lin:2011:LRB:2063016.2063042}.
